---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# coursedown

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/webbedfeet/coursedown.svg?branch=master)](https://travis-ci.org/webbedfeet/coursedown)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/webbedfeet/coursedown?branch=master&svg=true)](https://ci.appveyor.com/project/webbedfeet/coursedown)
<!-- badges: end -->

The goal of coursedown is to create a template for course materials. 

One folder (`slides`) comprises of lecture slides written using `xaringan` and is processed
using RMarkdown into a mini-website, where the `index.Rmd` would be a listing
of lectures as well as any meta-data related to lectures.

One folder (`notes`) comprises course notes (which may be derivative of the slides) built
using `bookdown` into a gitbook-formatted online book

One folder (`assignments`) can hold homework assignments written in RMarkdown

The top folder creates the class website using RMarkdown, which can link to 
a [Slack](http://www.slack.com) space for class collaboration, the [GitHub](http://www.github.com) repository for the course materials and 
various other pages (standard ones are provided for syllabus, instructor bio and
other resources)

## Installation


The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("webbedfeet/coursedown")
```
## Example

This is a basic example which shows you how to create a structured set of folders
based on `coursedown`:

```{r example, eval = F}
library(coursedown)
create_course(slides = T, notes = T, hw = F)

add_slide('00-Introduction.Rmd')
slide2note('slides/00-Introduction.Rmd', outdir = 'notes')
# This creates basic notes from the corresponding slides. These can now be
# edited before processing

process_notes(pdf=FALSE)
process_slides()

# or, all together
process(notes_pdf = FALSE)
```

